---
title: "Graphs"
output: html_notebook
---

# 0. Load Packages

```{r message=FALSE, results='hide'}
library(dplyr)
library(ggplot2)
library(ggrepel)
```

# 1. Load Data

```{r}
# Mom-level
data_moms <- read.csv("Data_Moms.csv", header = TRUE, fileEncoding = "UTF-8-BOM")

## Subset mom-level data to patches with hummingbird captures
data_moms_hummingbirds <- dplyr::filter(data_moms, Pop %in% c(10, 16, 19, 32, 33, 35, 40, 49, 50, 56, 58, 60, 63))

# Patch-level
data_patches <- read.csv("Data_Patches.csv", header = TRUE, fileEncoding = "UTF-8-BOM")

## Subset patch-level data to patches with hummingbird captures
data_patches_hummingbirds <- dplyr::filter(data_patches, Pop %in% c(10, 16, 19, 32, 33, 35, 40, 49, 50, 56, 58, 60, 63))
```

# 2. Proportion High-Mobility Hummingbirds vs. Deforestation Variables

## 2.1. Proportion of Forest

```{r}
plot_hummers_forest <- ggplot(data_patches_hummingbirds,
       aes(x = (Percent_Forest / 100), y = Proportion_High_Mobility)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  theme_classic(base_size = 20) +
  xlab("Proportion of Forested Area within 1-km") +
  ylab("Proportion High-Mobility Hummingbirds") +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  geom_point(size = 8, shape = 19) +
  annotate(geom = "text", x = 0.08, y = 0.8, label = "*", size = 15) +
  scale_y_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8)) +
  scale_x_continuous(breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7))
```

## 2.2. Patch Size

```{r}
plot_hummers_size <- ggplot(data_patches_hummingbirds,
       aes(x = log(Area_ha), y = Proportion_High_Mobility)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  theme_classic(base_size = 20) +
  xlab("Forest Patch Size [ha] (log transformed)") +
  ylab("") +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  geom_point(size = 8, shape = 19) +
  annotate(geom = "text", x = 0.5, y = 0.8, label = "**", size = 15) +
  scale_y_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8)) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7))
```

# 3. Haplotype Diversity (h) of Pollen Pools

## 3.1. vs. Proportion of High-Mobility Hummingbirds

```{r}
plot_pollen_hummers <- ggplot(data_moms_hummingbirds,
       aes(x = Proportion_High_Mobility, y = h_Pollen_Pool)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Proportion of High-Mobility Hummingbirds") +
  ylab(expression(paste("Haplotype Diversity (", italic("h"),") of Pollen Pools"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  annotate(geom = "text", x = 0.3, y = 0.6, label = "**", size = 15) +
  scale_y_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6)) +
  scale_x_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8))
```

## 3.2. vs. Patch Size

```{r}
#### 30 patches
plot_pollen_size_158 <- ggplot(data_moms,
       aes(x = log(Area_ha), y = h_Pollen_Pool)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Forest Patch Size [ha] (log transformed)") +
  ylab(expression(paste("Haplotype Diversity (", italic("h"),") of Pollen Pools"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  annotate(geom = "text", x = -0.5, y = 0.6, label = "**", size = 15) +
  scale_y_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6)) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7))

### 13 Patches
plot_pollen_size_73 <- ggplot(data_moms_hummingbirds,
       aes(x = log(Area_ha), y = h_Pollen_Pool)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Forest Patch Size [ha] (log transformed)") +
  ylab(expression(paste("Haplotype Diversity (", italic("h"),") of Pollen Pools"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  annotate(geom = "text", x = 0.5, y = 0.6, label = "**", size = 15) +
  scale_y_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6)) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7))
```

## 3.3. vs. Proportion of Forest

```{r}
#### 30 patches
plot_pollen_forest_158 <- ggplot(data_moms,
       aes(x = Percent_Forest / 100, y = h_Pollen_Pool)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Proportion of Forested Area within 1-km") +
  ylab(expression(paste("Haplotype Diversity (", italic("h"),") of Pollen Pools"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  scale_y_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6)) +
  scale_x_continuous(breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7))

### 13 Patches
plot_pollen_forest_73 <- ggplot(data_moms_hummingbirds,
       aes(x = Percent_Forest / 100, y = h_Pollen_Pool)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Proportion of Forested Area within 1-km") +
  ylab(expression(paste("Haplotype Diversity (", italic("h"),") of Pollen Pools"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  scale_y_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6)) +
  scale_x_continuous(breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7))
```

# 4. Multilocus Outcrossing Rate (tm)

## 4.1. vs. Propotion High-Mobility Pollinators

```{r}
plot_outcrossing_hummers <- ggplot(data_moms_hummingbirds, aes(x = Proportion_High_Mobility, y = Outcrossing)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2, linetype = "dashed") +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Proportion of High-Mobility Hummingbirds") +
  ylab(expression(paste("Multilocus Outcrossing Rate (",italic(~t[m]),")"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  scale_y_continuous(breaks = c(0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  scale_x_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8))
```

## 4.2. vs. Patch Size

```{r}
#### 30 patches
plot_outcrossing_size_158 <- ggplot(data_moms,
       aes(x = log(Area_ha), y = Outcrossing)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Forest Patch Size [ha] (log transformed)") +
  ylab(expression(paste("Multilocus Outcrossing Rate (",italic(~t[m]),")"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  annotate(geom = "text", x = -0.5, y = 1.025, label = "*", size = 15) +
  scale_y_continuous(breaks = c(0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7))

### 13 Patches
plot_outcrossing_size_73 <- ggplot(data_moms_hummingbirds,
       aes(x = log(Area_ha), y = Outcrossing)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Forest Patch Size [ha] (log transformed)") +
  ylab(expression(paste("Multilocus Outcrossing Rate (",italic(~t[m]),")"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  scale_y_continuous(breaks = c(0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7))
```

## 4.3. vs. Proportion Forest

```{r}
#### 30 patches
plot_outcrossing_forest_158 <- ggplot(data_moms,
       aes(x = Percent_Forest / 100, y = Outcrossing)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Proportion of Forested Area within 1-km") +
  ylab(expression(paste("Multilocus Outcrossing Rate (",italic(~t[m]),")"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  scale_y_continuous(breaks = c(0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  scale_x_continuous(breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7))

### 13 Patches
plot_outcrossing_forest_73 <- ggplot(data_moms_hummingbirds,
       aes(x = Percent_Forest / 100, y = Outcrossing)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Proportion of Forested Area within 1-km") +
  ylab(expression(paste("Multilocus Outcrossing Rate (",italic(~t[m]),")"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  scale_y_continuous(breaks = c(0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  scale_x_continuous(breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7))
```

# 5. Biparental Inbreeding

## 5.1. vs. Proportion High-Mobility Hummingbirds

```{r}
plot_biparental_hummers <- ggplot(data_moms_hummingbirds, aes(x = Proportion_High_Mobility, y = Biparental_Inbreeding)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Proportion of High-Mobility Hummingbirds") +
  ylab(expression(paste("Biparental Inbreeding (",italic(~t[m] - t[s]),")"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  annotate(geom = "text", x = 0.3, y = 0.6, label = "**", size = 15) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6)) +
  scale_x_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8))
```

## 5.2. vs. Patch Size

```{r}
#### 30 patches
plot_biparental_size_158 <- ggplot(data_moms,
       aes(x = log(Area_ha), y = Biparental_Inbreeding)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Forest Patch Size [ha] (log transformed)") +
  ylab(expression(paste("Biparental Inbreeding (",italic(~t[m] - t[s]),")"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  annotate(geom = "text", x = -0.5, y = 0.6, label = "**", size = 15) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6)) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7))

### 13 Patches
plot_biparental_size_73 <- ggplot(data_moms_hummingbirds,
       aes(x = log(Area_ha), y = Biparental_Inbreeding)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Forest Patch Size [ha] (log transformed)") +
  ylab(expression(paste("Biparental Inbreeding (",italic(~t[m] - t[s]),")"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  annotate(geom = "text", x = 0.5, y = 0.6, label = "**", size = 15) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6)) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7))
```

## 5.3. vs. Proportion Forest

```{r}
#### 30 patches
plot_biparental_forest_158 <- ggplot(data_moms,
       aes(x = Percent_Forest / 100, y = Biparental_Inbreeding)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Proportion of Forested Area within 1-km") +
  ylab(expression(paste("Biparental Inbreeding (",italic(~t[m] - t[s]),")"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6)) +
  scale_x_continuous(breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7))

### 13 Patches
plot_biparental_forest_73 <- ggplot(data_moms_hummingbirds,
       aes(x = Percent_Forest / 100, y = Biparental_Inbreeding)) +
  geom_smooth(method = "lm", se = TRUE, color = "black", size = 2) +
  geom_point(size = 8, shape = 1) +
  theme_classic(base_size = 20) +
  xlab("Proportion of Forested Area within 1-km") +
  ylab(expression(paste("Biparental Inbreeding (",italic(~t[m] - t[s]),")"))) +
  theme(axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20)) +
  annotate(geom = "text", x = 0.08, y = 0.6, label = "*", size = 15) +
  scale_y_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6)) +
  scale_x_continuous(breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7))
```

# 6. Ploting Figures

## 6.1. Figure 1

```{r message=FALSE}
figure_1 <- ggpubr::ggarrange(plot_hummers_forest, plot_hummers_size, labels = c("A", "B"), ncol = 2, nrow = 1)

tiff("Figure_1.tiff", units = "in", width = 15, height = 8, res = 300)
figure_1
```

## 6.2. Figure 2

```{r message=FALSE}
figure_2 <- ggpubr::ggarrange(plot_pollen_hummers, plot_outcrossing_hummers, plot_biparental_hummers, labels = c("A", "B", "C"), ncol = 3, nrow = 1)

tiff("Figure_2.tiff", units = "in", width = 18.5, height = 6, res = 300)
figure_2
```

## 6.3 Supplementary Figure 2

```{r message=FALSE}
supp_figure_2 <- ggpubr::ggarrange(plot_pollen_size_158, plot_outcrossing_size_158, plot_biparental_size_158, plot_pollen_forest_158, plot_outcrossing_forest_158, plot_biparental_forest_158, labels = c("A", "B", "C", "D", "E", "F"), ncol = 3, nrow = 2)

tiff("Supp_Figure_3.tiff", units = "in", width = 18.5, height = 13, res = 300)
supp_figure_3
```

## 6.4. Supplementaty Figure 3

```{r message=FALSE}
supp_figure_3 <- ggpubr::ggarrange(plot_pollen_size_73, plot_outcrossing_size_73, plot_biparental_size_73, plot_pollen_forest_73, plot_outcrossing_forest_73, plot_biparental_forest_73, labels = c("A", "B", "C", "D", "E", "F"), ncol = 3, nrow = 2)

tiff("Supp_Figure_4.tiff", units = "in", width = 18.5, height = 13, res = 300)
supp_figure_4
```